A Survey of Real-Time Strategy Game AI\\ Research and Competition in StarCraft

### 2013-03-06 survey.tex
Added title
updated title
Added a draft of the conclusions

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{TODO: A Survey of StarCraft AI Techniques}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

An initial attempt to run a StarCraft tournament at the Computational
Intelligence in Games conference 2010 suffered from technical problems.
These mainly stemmed from the desire to use evolved, largely untested
maps which proved to look interesting but made the submitted bots 
(and/or the Broodwar Terrain Analyzer (BWTA) provided with the BWapi interface) crash
so frequently that it would have been unjustifiable to announce a winner.

@@

\item {\bf Learning and adaptation:}
\begin{itemize}
\item Adaptation to opponent strategy: observing the opponent strategy, and synthesizing an adequate counter strategy. Current bots switch between predefined strategies based on hard-coded preconditions, or based on the performance of each predefined strategy against an opponent in previous games, but no current bot creates new strategies (like Chess or Go playing programs do).
\item Learning from experience in RTS games: how can we make a bot that improves performance over time? some current bots learn which strategy (out of a predefined set of strategies) is best against a given opponent, but how can we devise learning strategies that can perform more general learning?
\item Learning from observation (from demonstration, or from observing the opponent) in RTS games: how can we learn by observing the game play of other players? can we devise algorithms that can automatically extract strategies from observation, and later apply them?
\end{itemize}

@@

\section{Discussion and Conclusions}\label{sec:conclusions}

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{A Survey of Real-Time Strategy Game AI\\ Research and Competition in StarCraft}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

An initial attempt to run a StarCraft tournament at the Computational
Intelligence in Games conference 2010 suffered from technical problems.
These mainly stemmed from the desire to use evolved, largely untested
maps which proved to look interesting but made the submitted bots 
(and/or the Broodwar Terrain Analyzer (BWTA) provided with the BWAPI interface) crash
so frequently that it would have been unjustifiable to announce a winner.

@@

\item {\bf Learning and adaptation:}
\begin{itemize}
\item Adaptation to opponent strategy: observing the opponent strategy, and synthesizing an adequate counter strategy. Current bots switch between predefined strategies based on hard-coded preconditions, or based on the performance of each predefined strategy against an opponent in previous games, but no current bot creates new strategies (like Chess or Go playing programs do).
\item Learning from experience in RTS games: how can we make a bot that improves performance over time? some current bots learn which strategy (out of a predefined set of strategies) is best against a given opponent, but how can we devise learning strategies that can perform more general learning? This has been achieved in classical board games, such as Chess~\cite{tesauro2001comparison}, in the context of game-tree search (by learning the evaluation function). But it's unclear how to do it in RTS games.
\item Learning from observation (from demonstration, or from observing the opponent) in RTS games: how can we learn by observing the game play of other players? can we devise algorithms that can automatically extract strategies from observation, and later apply them? There has been some work in this direction \cite{OntanonMSR10}, but it is very far from being mature.
\end{itemize}

@@

\section{Conclusions}\label{sec:conclusions}

As the list in the previous section indicates, Real-Time Strategy games are an excellent testbed for AI techniques, which pose a very large list of open problems. As Section \ref{sec:competition} has shown, the current top performing programs to play RTS games such as StarCraft still rely mainly on hard-coded strategies. It is still possible to perform strongly, or even win, one of these competitions simply by finding a hard-coded strategy that no other bot has a predefined counter-strategy for. Additionally, good human players are still clearly superior to the best computer programs.

One of the main goals of this paper is to provide a centralized and unified overview to the research being done in the area of RTS game AI. To that end, in this paper we have tried to highlight the existing challenges in RTS games, from an AI point of view, and survey the recent advances towards addressing these challenges, with a focus on StarCraft, which has emerged as a unified test-bed. Given that playing an RTS game is a very challenging task, researchers tend to divide such task into smaller tasks, that can be individually addressed by AI techniques. We have also surveyed the different task subdivisions used in some of the top StarCraft-playing programs, highlighting advantages and disadvantages. Additionally, we have presented an analysis of the results of the different StarCraft AI competitions, highlighting strengths and weaknesses of each of the bots. Finally, we have closed the paper with a list of specific open research questions for future research.

As argued before, addressing these open research questions would not just lead to better RTS game playing bots. Since RTS games embody many characteristics of many other problems appearing in many areas of AI (such as robotics, multiagent systems, etc.), addressing these questions would also benefit many other areas of AI.
